FireSim2019_ManuscriptFigures

### 2023-03-16 README.rmd

>>>>

Combined_Lab_Field_OTU_table.csv: R dataframe of OTUs in the combined lab experiment/field datasets

Combined_Lab_Field_sample_data.csv: R dataframe of sample names and metadata for the combined lab experiment/field datasets

Combined_Lab_Field_tax_table.csv: R dataframe of taxonomy table for combined lab experiment/field datasets

lab_OTU_table.csv: R dataframe of OTUs in the lab experiment datasets

lab_sample_data.csv: R dataframe of sample names and metadata for the lab experiment datasets

lab_taxonomy_table.csv: R dataframe of taxonomy for lab experiment datasets
